\documentclass[10pt]{report}
\begin{document}
\author{}
MAKERERE UNIVERSITY COLLEGE OF COMPUTING AND INFORMATION SCIENCE
\\\
\\\
RESEARCH METHODOLOGY ASSIGNMENT
\\\
\\\
\author{}
OCHAN JULIUS JOSHUA
\\\ 
REG NO 12/U/13092/EVE
\\\

\title{}
DATA COLLECTION ON STUDENT RESULT COMPLAINT SYSTEM
\section{Introduction}

\paragraph{The following are my findings during the time I was conducting/carrying out my data collection on the student result complain system asking them of how the old system works and what they would prefer. This what I did in order to get information from them.}
\subsection{Activities  done}
\paragraph{I distributed questionnaires within the college of computing and information science which was my target area as system users and here I was able to collect my data from different students doing different courses at the faulty. The pie chart below shows my finding from the students.
Out of the total of students we had given the questionnaire to, 14 percent who had complained got their results updated in time, 50 percent reported delayed response to their complaints thus most of them got discourage on using the current system at hand and the remaining 26 percent of the students reported having complained and didn't get any response. They ended up redoing their respective course units.I also had 10 percent student out of the student we gave questionnaire to reporting no issues with their results.
}
\subsection{Problems /outcomes}
\paragraph{It was very had to get student who would allow me to take their photos and record their voice or have their expression in video format.\\
}
\subsection{sample questions used in the questionnaire}
\begin{enumerate}
\item 
1.Have you ever joined and studied in any University?\\\
Yes\\\
No.
\\\
2.	Have you ever sat for any examination, test or done any coursework?\\\
Yes\\\
No
\\\
3.	If yes have you ever had issues with your marks missing?\\\
Yes\\\

No
\\\
4.	If yes how did you handle it?
………………………………………………………………………………………………………………………………………………………………………………………………
\\\
5.	Have you ever complained about missing marks and how did you do it?\\\
Manual complaint.\\\
online complaint.\\\
\\\
6.	If manual have you ever got any update about your complain or any information of where you complain has reached?\\\
Yes\\\

No
\\\
7.	If yes how did you receive the update or feedback of your complained and from who?
………………………………………………………………………………………………………………………………………………………………………………………………
\\\
8.	How long did it take for your results to be updated\\\

One week\\\
Full semester.\\\

Not at all.\\\
\\\
9.	Have you ever used any online complained management system?\\\
Yes \\\
No
\\\
10.	If yes what was your experienced with the system?
………………………………………………………………………………………………
\\\
11.	If no what would your system suggestion be, between the online and manual system of results complaint system?
………………………………………………………………………………………………………………………………………………………………………………………………What is your past experience with the issue of missing marks, specify briefly?
………………………………………………………………………………………………………………………………………………………………………………………………
\\\
12.	What do you think about having ansms or email base system to update or track results complaints?\\\
                   Fast\\\
                    Slow\\\
     Waste of time\\\

None.
\\\
Please suggest any other possible way you think the complained systems can be made morinteractive and user friendly,briefly?
……………………………………………………………………………………………………………………………………………………………………………………………………
\\\
\\\
Thank for your time and response






\end{enumerate}



\end{document}